Commit Rater

### 2015-08-25 presentations/paper/conclusion.tex
Comment out instructions in Conclusion

\section{Conclusion}

This is essentially a redundant section. Try to summarize your
research from a more informed point of view. (We assume that the
reader has read the paper and is ready for some deeper conclusion.)
You could very well add some perspectives for future work, without
repeating smaller scale weakness of research, as they were already
identified in the threats to validity section.

>>>>

\section{Conclusion}
\label{sec:conclusion}

%This is essentially a redundant section. Try to summarize your
%research from a more informed point of view. (We assume that the
%reader has read the paper and is ready for some deeper conclusion.)
%You could very well add some perspectives for future work, without
%repeating smaller scale weakness of research, as they were already
%identified in the threats to validity section.
